Functory: Une bibliothèque de calcul distribué \\ pour Objective Caml\footnotetext{Ce travail a été réalisé en partie dans le cadre du projet U3CAT (\emph{Unification of Critical C Code Analysis Techniques}, ANR-08-SEGI-021).}

### 2010-10-21 doc/jfla-2011/main.tex
*** empty log message ***

% \hrulefill ICI\hrulefill

\section{Implementation Details}\label{sec:implem}

We now describe the implementations of the various modules introduced
in Section~\ref{sec:API}. The implementation of the \of{Sequential}
module is straightforward and does not require any explanation.

\subsection{Multiple Cores}

@@

The \of{Cores} module is implemented with \unix\ processes, using the
\of{fork} and \of{wait} system calls provided by the \of{Unix} library
of \Ocaml. The idea is pretty simple.  The \of{compute} function
maintains a global table of pending tasks and keeps track of the
number of idle cores.  Whenever there is a pending task and an idle
core, a new sub-process is created using \of{Unix.fork}; once
completed, the sub-process marshals the result into a 
local file. The
main process maintains a table mapping each sub-process ID to the
input task and the local file name. It waits for any completed
sub-process using \of{Unix.wait} and recovers the result from the
local file. Then function \of{master} is applied, which may generate
new tasks.  The main loop can be depicted in the following way:
\begin{flushleft}
  \quad  \textbf{while} pending tasks $\lor$ pending sub-processes \\
  \quad  \quad \textbf{while} pending tasks $\land$ idle cores \\
  \quad  \quad \quad create new sub-process for some task \\
  \quad  \quad \textbf{wait} for any completed sub-process \\
  \quad  \quad \quad push new tasks generated by \of{master} \\
\end{flushleft}
We also have an alternative implementation using
\unix\ pipes instead of local files.

@@

\subsection{Network of Machines}

>>>>

\section{Détails techniques}\label{sec:implem}

Cette section décrit la réalisation des différents modules de la
bibliothèque \functory\ introduits section~\ref{sec:API}, exception
faire du module \of{Sequential}, dont la réalisation est immédiate.

\hrulefill ICI\hrulefill

Les deux modules \of{Cores} et \of{Network}

\begin{flushleft}
  \quad  \textbf{tant que} tâches à faire $\lor$ tâches en cours \\
  \quad  \quad \textbf{tant que} tâches à faire $\land$ ouvriers disponibles \\
  \quad  \quad \quad affecter une tâche à un ouvrier \\
  \quad  \quad \textbf{attendre} la fin d'une tâche \\
  \quad  \quad \quad ajouter les nouvelles tâches renvoyées par \of{master} \\
\end{flushleft}

\subsection{\of{Cores}}

@@

The \of{Cores} module is implemented with \unix\ processes, using the
\of{fork} and \of{wait} system calls provided by the \of{Unix} library
of \Ocaml. The idea is pretty simple.  The \of{compute} function
maintains a global table of pending tasks and keeps track of the
number of idle cores.  Whenever there is a pending task and an idle
core, a new sub-process is created using \of{Unix.fork}; once
completed, the sub-process marshals the result into a 
local file. The
main process maintains a table mapping each sub-process ID to the
input task and the local file name. It waits for any completed
sub-process using \of{Unix.wait} and recovers the result from the
local file. Then function \of{master} is applied, which may generate
new tasks.  The main loop can be depicted in the following way:

We also have an alternative implementation using
\unix\ pipes instead of local files.

@@

\subsection{\of{Network}}
